---
title: Report on quarto submissions with unexpectedly similar texts
date: today
format:
  html:
    embed-resources: true
    code-tools: true
    code-fold: true
params:
  html_dir: ""
  threshold: 0.7
execute:
  echo: true

---

```{r}
#| label: setup
#| code-summary: Code - Load package
library(qpcontrol)
```


- extract qmd
- report any submitted only as qmd (rendering problems??)
- report empty files (text reuse would do this, but awkward in flow)
- plot dendrogram with threshold
- iterate through pairs of documents with dissimilarity < threshold



```{r}
#| label: extract
#| code-summary: Code - Extract qmd

# directory to store the files
tmp <- tempdir()
txt_path <- file.path(tmp, "txt")
fs::dir_create(txt_path)

# extract qmd from html files
qp_extract(html_dir = params$html_dir, txt_dir = txt_path)
```

Possible problems at this stage include: students submitting the qmd file rather than the html file, not using code-tool argument, having some formatting error that prevents code-tools from functioning properly. 

Next version of this package will try to address these problems.

Now we can use `qp_pairwise()` to convert each document to overlapping n-grams and find the Jaccard similarity between pairs of documents.
This function is a wrapper for the `textreuse` package.

```{r}
#| label: calculate-distances
#| code-summary: Code - Calculate distances
txt_distances <- qp_pairwise(txt_dir = txt_path)
attr(txt_distances, "skipped")
```

This result is a distance matrix which can be clusters with `hclust()`.
Pairs of submissions with unexpectedly low dissimilarity need to be checked for possible plagiarism.

```{r}
#| label: fig-distances
#| code-summary: Code - Plot distances
h_single <- t(txt_distances) |>
  as.dist() |>
  hclust(method = "single") 
h_single |>
  plot(labels = 1:nrow(txt_distances))
abline(h = params$threshold, lty = 2, col = 2)
```

### outliers

```{r}
#| label: most-unique
cut <- h_single |> 
  cutree(k = 2)
names(cut)[cut == which.min(table(cut))]
```



Possible pairs can be identified with `which()`

```{r}
#| label: distances-gt-thresh
#| code-summary: Code - Find distances below threshold
results <- qp_which(txt_distances, params$threshold)
results
```


The `qp_diffr()` function uses the `diffr` package to compare texts.


```{r}
#| label: show-differences
#| code-summary: Code - Show first pair
#| output: asis
if (nrow(results) > 0) {
  cat(paste("# Case 1"))
  qp_diffr(results[1, ], txt_dir = txt_path)
}
```

Check for overlap because assignment text is repeated.


```{r}
#| label: show-more-differences
#| code-summary: Code - Show remaining pairs
#| output: asis
if (nrow(results) > 1) {
  for (i in 2:nrow(results)) {
    cat(paste("\n# Case ", i, "\n"))
    qp_diffr(results[i, ], txt_dir = txt_path) |> print()
  }
}
```

